Distance Sampling in \proglang{R}

### 2016-06-08 paper.Rnw
table captions below

@@

\begin{figure}
\begin{center}
<<label=amakihiqq, echo=FALSE, message=FALSE, fig.height=3, fig.width=6, results="hide">>=
par(mfrow=c(1,2))
gof_ds(amakihi_hn, asp=1, cex=0.3)  # shrinking dot size to obliterate 45-deg line less
gof_ds(amakihi_hr_obs_mas, asp=1, cex=0.3)
@
\caption{Comparison of quantile-quantile plots for a half-normal model (no adjustments, no covariates; left) and hazard-rate model with observer and minutes after sunrise (right) for the amakihi data.}
\label{amakihi-qq}
\end{center}
\end{figure}

@@

\begin{table}
\begin{tabular}{ccccc}
Feature    &  \pkg{Distance} & \pkg{Rdistance} & \pkg{unmarked} & \pkg{mrds}\\
\hline
Line transects & x & x & x & x\\
Point transets & x & & x & x\\
Interval (binned) distances & x & & x & x\\
Exact distances & x & x & & x\\
Continuous individual level covariates & x &  & & x\\
Factor individual level covariates & x & x & & x\\
Transect level covariates & x &  & x & x\\
Objects in clusters & x & x & x & x\\
Left truncation & x  & x & & x\\
Half-normal key & x & x & x & x\\
Hazard-rate key & x & x &  x & x\\
Uniform key & x & x & x & x\\
Gamma key &  & x &  & x\\
Negative exponential key &  &  & x  &\\
Adjustment terms & x & x & & x\\
AIC adjustment selection & x & x & \\
Monotonicity constraints & x &  & & x\\
Availability bias model & & & x &\\
Perception bias model & & & & x\\
Abundance estimation & x & x & x & x\\
Density estimation & x & x & x & x\\
User-defined likelihood functions & & x & & \\
\end{tabular}
\caption{Feature comparison of the available packages to perform distance sampling analyses.}
\label{app-comp-tab}
\end{table}

>>>>

% make captions be at the bottom
\usepackage{float}
\floatstyle{plain}
\restylefloat{table}

@@

\begin{figure}
\begin{center}
<<label=amakihiqq, echo=FALSE, message=FALSE, fig.height=4, fig.width=7, results="hide">>=
par(mfrow=c(1,2))
gof_ds(amakihi_hn, asp=1, cex=0.3)  # shrinking dot size to obliterate 45-deg line less
gof_ds(amakihi_hr_obs_mas, asp=1, cex=0.3)
@
\caption{Comparison of quantile-quantile plots for a half-normal model (no adjustments, no covariates; left) and hazard-rate model with observer and minutes after sunrise (right) for the amakihi data.}
\label{amakihi-qq}
\end{center}
\end{figure}

@@

\begin{table}[h]
\begin{tabular}{ccccc}
Feature    &  \pkg{Distance} & \pkg{Rdistance} & \pkg{unmarked} & \pkg{mrds}\\
\hline
Line transects & x & x & x & x\\
Point transets & x & & x & x\\
Interval (binned) distances & x & & x & x\\
Exact distances & x & x & & x\\
Continuous individual level covariates & x &  & & x\\
Factor individual level covariates & x & x & & x\\
Transect level covariates & x &  & x & x\\
Objects in clusters & x & x & x & x\\
Left truncation & x  & x & & x\\
Half-normal key & x & x & x & x\\
Hazard-rate key & x & x &  x & x\\
Uniform key & x & x & x & x\\
Gamma key &  & x &  & x\\
Negative exponential key &  &  & x  &\\
Adjustment terms & x & x & & x\\
AIC adjustment selection & x & x & \\
Monotonicity constraints & x &  & & x\\
Availability bias model & & & x &\\
Perception bias model & & & & x\\
Abundance estimation & x & x & x & x\\
Density estimation & x & x & x & x\\
User-defined likelihood functions & & x & & \\
\end{tabular}
\caption{Feature comparison of the available packages to perform distance sampling analyses.}
\label{app-comp-tab}
\end{table}
